Functional oxide layers for electrical isolation and chemical passivation of steel substrates

### 2023-03-05 Thesis/chapter/030-theory-materials.tex
proof read until KRR

\pagebreak[4]
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%   SEM    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Scanning electron Microscopy}
The history of \gls{sem} can be traced back to 1843 when Scottish clockmaker Alexander Bain filed a patent for dissecting an image by scanning. 
The first \gls{sem} was build in 1933, 
the first images from scanning electron beams were published in 1935
and the first \gls{sem} was marketed in 1965.
A more detailed history of \gls{sem} can be read in a open-to-read paper by McMullan from 1995\cite{McMullan1995}. 
\Gls{sem} is a microscopical technique which allows visualisation of surfaces with features in the nano meter regime. 
While optical microscopes use visible light and optical lenses, \gls{sem} uses accelerated electron beams and electrostatic and electromagnetic lenses.
This allows the generation of much more detailed images due to the shorter wavelengths of electrons compared to visible light\cite{Kaliva2020}.
The electron beam produces X-rays, elastically backscattered (primary) electrons, inelastic (secondary) electrons and Auger electrons. 
Secondary electrons carry information to conclude morphology and topology of the sample while X-rays can be used to identify the elements. 
Electrons originate from either a \gls{feg}, where a strong electrical field rips electrons from the bulk, or from thermionic guns where the filament (tungsten W or \ch{LaB6} (brighter and longer lasting but more expensive)) is heated until electrons are emitted. 
Electrons are then accelerated by a voltage of \SI{2}{\kilo\volt} to \SI{40}{\kilo\volt} and bundled into narrow beams by lenses\cite{Vernon2000}.
A high mean free path is needed for electrons to travel from the source to the sample (and to the detector). 
Thus, a very low pressure is needed inside the microscope. 
In this work \gls{sem} was used as a preliminary way of checking the quality of \gls{zro} layer. 
% squeeze condition into this page 
\enlargethispage{\baselineskip}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{UV/Vis/NIR Spectroscopy}
%%% WHAT? 
\Gls{uv}/\gls{vis}/\gls{nir} spectroscopy is a molecular spectroscopic method using 
interactions of \gls{uv}, \gls{vis} and \gls{nir} light 
(wavelengths of \num{e-7} to \num{e-6}\m{}) with molecules\cite{Schwedt2008}.
In general, light is described as periodic \gls{em} wave 
which - in vacuum - moves with the speed of light ($c = \mps{299792458}$).
In other materials light moves with the velocity $v=\frac{c}{n(\lambda)}$, where $n(\lambda)$ is the refractive index which is a function of the wavelength $\lambda$. 
The relation of the energy of a photon~$E$, its frequency~$\nu$, wavelength~$\lambda$ and wave number~$\bar{\nu}$ are as follows:
\begin{align*}
	E &= h \cdot \nu \\
	\nu &= c/ \lambda \\
	\bar{\nu} &= 1/\lambda,
\end{align*}
where $h$ is the Planck's constant.
%In words: shorter wavelength (higher frequency) photons are more energetic.
In practice the spectrum of \gls{em} waves is sectioned into different ranges; % (\td{see figure?+table});
from high to low energy: X-ray, \gls{uv}, \gls{vis}, (near, middle and far) \gls{ir}, microwaves and radio waves. 
X-rays interact with core electrons, \gls{uv}\gls{vis} with valence electrons, \gls{ir} with molecular vibrations, microwaves with molecular rotations and radio with electron and nuclear spins. 
%Molecular vibrations can be separated in valence and deformation vibrations.

% UVVis
Two prerequisites need to be fulfilled in order for a \gls{uv}\gls{vis} photon to be 
absorbed by a molecule or atom.
Firstly, the energy must be the same as the difference between two electronic states, a lower populated and a higher empty orbital. 
The electron will then be excited into a energetically higher orbital.
Secondly, the spin state of both states has to be the same otherwise the transition is "forbidden" and the absorption is extremely unlikely.

% IR
\Gls{ir} photons interact with molecular vibrations, which is only a part of the degrees of freedom of a molecule.
A molecule has $F=3N$ ($N$ number of atoms) degrees of freedom, including translational $F_T=3$ and rotational $F_R=3$ (2 for linear molecules) movements. 
%
The number of vibrations can therefore be calculated as 
\begin{align*}
	F_V &= 3N - F_T - F_R = 3N - 6 \\
	F_V &= 3N - F_T - F_R = 3N - 5 \textrm{ (for linear molecules)}.
\end{align*}
Vibrations are classified in valence vibrations (change of bond length) and deformation (change of bond angle) vibrations\cite{Melker2006}. 
Only vibrations that change the dipole moment of the molecule are \gls{ir} active. 
The absorption of \Gls{nir} electromagnetic waves involves excitations of non-fundamental vibrations, overtones and combination modes. 
These transition are mostly "forbidden" quantum mechanically and allow analysis of bulk matter without extensive preparation
due to the deep penetration depth of \gls{nir} light\cite{bec2019breakthrough}.

@@

\paragraph{Fourier Transform Spectrometer}
 %A ceramic material (Nernst glower) is heated to around \oc{1600} as light source. 
In the classic two-beam-spectrometer the light emitted from the light source is split, 
sent through the sample and the reference and one of the two beams is alternately 
sent through a monochromator to a detector (often a thermopile).
%
In the \gls{ft} spectrometer the beam is sent through the sample, split and 
reflected from a static and from a moving mirror, recombined and detected by a photo 
multiplier (a device which transforms photons into electrical signals). 
How the two beams will interfere upon recombination depends on the optical path difference (also called retardation) of the two light beams\cite{Schwedt2008}.
In a \gls{ft} spectrometer the reference has to be measured before the sample.
%
When the refractive index of two layers differ, light can be used to measure the thickness\cite{Dumin1967} of the optical less dense material.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{X-Ray Diffraction}
%\url{https://link.springer.com/content/pdf/10.1186/2228-5326-3-8.pdf}
\gls{xrd} is used to study the crystalline structure of materials.
Since X-rays wavelengths (\num{0.2} to \nm{10}) are comparable to the interatomic spacing of crystalline solids the beams get reflected and contain information about the structure\cite{Kaliva2020}.
Each crystalline material has a discreet atomic structure, which upon irradiation with 
X-rays causes constructive and destructive interference according to Bragg's law and generates unique diffraction patterns. 
\Gls{xrd} diffraction plots of crystalline materials feature distinct peaks, whereas amorphous materials exhibit a broad curve with a maximum extending over several degrees (2$\theta$).

>>>>

\pagebreak[4]
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%   SEM    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Scanning electron Microscopy}
The history of \gls{sem} can be traced back to 1843 when Scottish clockmaker Alexander Bain filed a patent for dissecting an image by scanning. 
The first \gls{sem} was build in 1933, 
the first images from scanning electron beams were published in 1935
and the first \gls{sem} was marketed in 1965.
A more detailed history of \gls{sem} can be read in a open-to-read paper by McMullan from 1995\cite{McMullan1995}. 
\Gls{sem} is a microscopical technique which allows visualisation of surfaces with features in the nano meter regime. 
While optical microscopes use visible light and optical lenses, \gls{sem} uses accelerated electron beams and electrostatic and electromagnetic lenses.
This allows the generation of much more detailed images due to the shorter wavelengths of electrons compared to visible light\cite{Kaliva2020}.
The electron beam produces X-rays, elastically backscattered (primary) electrons, inelastic (secondary) electrons and Auger electrons in the examined material. 
Secondary electrons carry information to conclude morphology and topology of the sample while X-rays can be used to identify the elements. 
Electrons originate from either a \gls{feg}, where a strong electrical field rips electrons from the bulk, or from thermionic guns where a filament (tungsten W or \ch{LaB6} (brighter and longer lasting but more expensive)) is heated until electrons are emitted. 
Electrons are then accelerated by a voltage of \SI{2}{\kilo\volt} to \SI{40}{\kilo\volt} and bundled into narrow beams by lenses\cite{Vernon2000}.
A high mean free path is needed for electrons to travel from the source to the sample (and to the detector). 
Thus, a very low pressure is needed inside the microscope. 
In this work \gls{sem} was used as a preliminary way of checking the quality of \gls{zro} layer. 
% squeeze condition into this page 
\enlargethispage{\baselineskip}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{UV/Vis/NIR Spectroscopy}
%%% WHAT? 
\Gls{uv}/\gls{vis}/\gls{nir} spectroscopy is a molecular spectroscopic method using 
interactions of \gls{uv}, \gls{vis} and \gls{nir} light 
(wavelengths of \num{e-7} to \num{e-6}\m{}) with molecules\cite{Schwedt2008}.
In general, light is described as periodic \gls{em} wave 
which - in vacuum - moves with the speed of light ($c = \mps{299792458}$)\cite{gHobel2006international}.
In other materials light moves with the velocity $v=\frac{c}{n(\lambda)}$, where $n(\lambda)$
is the refractive index which is dependent on the wavelength $\lambda$. 
%is the refractive index which is a function of the wavelength $\lambda$. 
The relation of the energy of a photon~$E$, its frequency~$\nu$, wavelength~$\lambda$ and wave number~$\bar{\nu}$ are as follows:
\begin{align*}
	E &= h \cdot \nu \\
	\nu &= c/ \lambda \\
	\bar{\nu} &= 1/\lambda,
\end{align*}
where $h$ is Planck's constant.
%In words: shorter wavelength (higher frequency) photons are more energetic.
In practice the spectrum of \gls{em} waves is sectioned into different ranges; % (\td{see figure?+table});
from high to low energy: X-ray, \gls{uv}, \gls{vis}, (near, middle and far) \gls{ir}, microwaves and radio waves. 
X-rays interact with core electrons, \gls{uv}\gls{vis} with valence electrons, \gls{ir} with molecular vibrations, microwaves with molecular rotations and radio with electron and nuclear spins. 
%Molecular vibrations can be separated in valence and deformation vibrations.
%
% UVVis
Two prerequisites need to be fulfilled in order for a \gls{uv}\gls{vis} photon to be 
absorbed by a molecule or atom.
Firstly, the energy must be the same as the difference between two electronic states, a lower populated and a higher empty orbital. 
The electron will then be excited into a energetically higher orbital.
Secondly, the spin state of both states has to be the same otherwise the transition is "forbidden" and the absorption is extremely unlikely.

% IR
\Gls{ir} photons interact with molecular vibrations, which is only a part of the degrees of freedom of a molecule.
A molecule has $F=3N$ ($N$ number of atoms) degrees of freedom, including translational $F_T=3$ and rotational $F_R=3$ (2 for linear molecules) movements. 
%
The number of vibrations can therefore be calculated as 
\begin{align*}
	F_V &= 3N - F_T - F_R = 3N - 6 \\
	F_V &= 3N - F_T - F_R = 3N - 5 \textrm{ (for linear molecules)}.
\end{align*}
Vibrations are classified in valence vibrations (change of bond length) and deformation (change of bond angle) vibrations\cite{Melker2006}. 
Only vibrations that change the dipole moment of the molecule are \gls{ir} active. 
The absorption of \Gls{nir} electromagnetic waves involves excitations of non-fundamental vibrations, overtones and combination modes which lead to intricate patterns called the fingerprint region. 
These transition are mostly "forbidden" quantum mechanically and allow analysis of bulk matter without extensive preparation
due to the deep penetration depth of \gls{nir} light\cite{bec2019breakthrough}.

@@

\subsubsection{Fourier Transform Spectrometer}
 %A ceramic material (Nernst glower) is heated to around \oc{1600} as light source. 
In the classic two-beam-spectrometer the light emitted from the light source is split, 
sent through the sample and the reference and one of the two beams is alternately 
sent through a monochromator to a detector (often a thermopile).
%
In the \gls{ft} spectrometer the beam is sent through the sample, split and 
reflected from a static and from a moving mirror, recombined and detected by a photo 
multiplier (a device which transforms photons into electrical signals). 
How the two beams will interfere upon recombination depends on the optical path difference (also called retardation) of the two light beams\cite{Schwedt2008}.
In a \gls{ft} spectrometer the reference has to be measured before the sample.
%
%When the refractive index of two layers differ, light can be used to measure the thickness\cite{Dumin1967} of the optical less dense material.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{X-Ray Diffraction}
%\url{https://link.springer.com/content/pdf/10.1186/2228-5326-3-8.pdf}
\gls{xrd} is used to study the crystalline structure of materials.
Since X-rays wavelengths (\num{0.2} to \nm{10}) are comparable to the interatomic spacing of crystalline solids, 
the beams get reflected and contain information about the structure\cite{Kaliva2020}.
Each crystalline material has a discreet atomic structure, which upon irradiation with 
X-rays causes constructive and destructive interference according to Bragg's law and generates unique diffraction patterns. 
\Gls{xrd} diffraction plots of crystalline materials feature distinct peaks, whereas amorphous materials exhibit a broad curve with a maximum extending over several degrees (2$\theta$).

### 2023-03-05 Thesis/chapter/031-theory-calculations.tex
proof read until KRR

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Machine Learning and Statistics}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Why introduce machine learning to this project? 
%I wanted to apply and delve into what I've been studying during my undergrad courses. 
%This seemed like the perfect oppurtunity. 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Is machine learning just hyped statistics? No! 
		%{https://doi.org/10.1177\%2F1352458520978648}
		%{Machine and deep learning in MS research are just powerful statistics – No}
%What is \gls{ml}? 
Some might argue that \gls{ml} is just overglorified statistics, but that's not the case. 
Although \gls{ml} uses several statistical methods, their goal and frame conditions are different. 
%\td{The goal of machine learning is to ???}
%
\Gls{ml} tries to predict unseen data points accurately and statistics is a subfield of maths 
which tries to get insight into a given data. 
For example, in a statistical model, it is desirable to reduce the number of inputs. 
This allows the statistician to better study how a change in the input variable can be 
directly affected by the output variable.\cite{gontcharov2019}
%pic from \url{https://towardsdatascience.com/notes-on-artificial-intelligence-ai-machine-learning-ml-and-deep-learning-dl-for-56e51a2071c2}
More precisely, mathematical statistics (stochastic)\cite{haertler2014statistisch} is the subject of 
finding mathematical models to describe the data 
whereas (classical) statistics is the domain of representing the data. 
Nonetheless, statistics and maths is at the basis of \gls{ml}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Artificial Inteligence and Machine Learning}
%How can \gls{ai} and \gls{ml} be defined? 
\Gls{ai} is a trans-disciplinary field with roots in logic, statistics, cognitive psychology, decision theory, neuroscience, linguistics, cybernetics, and computer engineering\cite{howard2019artificial}.
The history of \gls{ai} goes back to the middle of the \nth{20} century. 
Researchers from the emerging field came together at the Dartmouth conference and the term "\gls{ai}" was coined\cite{McCarthy1955}. 
\Gls{ai}'s  history is beautifully depicted by McCorducks' 1982 book "Machines Who Think"\cite{McCorduck1982,Apter1982}, which focuses on the great minds behind the advances.
Pioneers like Alan Turing thought a lot about how to define, test and implement \gls{ai}\cite{howard2019artificial}. 
One example how to measure \gls{ai} is to let it play chess against a human\cite{Silver2017} 
(in 1997 a chess computer called Deep Blue won against the World Chess Champion Garry Kasparov for the first time\cite{Feng1999}).
Another test \textit{ingenioused} by Alan Turing is the imitation game\cite{turing1950imitation}, nowadays known as Turing test:
an interrogator communicates with two unknown entities \textbf{A} and \textbf{B} (a woman and a man) and must find out who is who. 
\textbf{A} will try to make to interrogator misjudge, whereas \textbf{B} is on the interrogators side.
The question is if \textbf{A} is replaced with a computer how the ratio of outcomes would deviate from the original ratio. 
%
At the moment it's hard to imagine a computer getting a higher ratio than a human
but when reading AI written articles\cite{gpt2020}, it's easy to see this test being passed in the future.

But fear not, that doesn't mean that computers are sentient or more intelligent than humans\cite{searle1980,searle1999married} even though some claim\cite{tiku2022google} and it certainly does not mean that research is over. 
AI is still a young field, which is strongly growing and is gaining ubiquitous status. 
It is slowly creeping into every aspect of modern human life just like electricity around one hundred years ago. 
Realms in which AI is gaining traction are: 
%
playing board games (and beating humans)\cite{Silver2017,Feng1999,Campbell2002}, 
image recognition (very popular for medical diagnosis)\cite{Li2020,Deo2015,Topol2019,Fujiyoshi2019}, 
chemistry\cite{Westermayr2019,goh2017chemception,jha2018elemnet}, 
cyber security\cite{Sarker2021},
facial recognition (to prevent theft of toilet paper \cite{Andrews2017}),
financial sector (as robo-advisors)\cite{Littman2021},
natural language processing (NLP)\cite{Koroteev2021,Liu2021gpt,Parviainen2021} 
(which can also create code and pictures through scalable vector graphics (SVG))
and even creative tasks like 
creating non existing faces\cite{Mansourifar2020}, 
create graphic artwork (DALL-E 2)\cite{Marcus2022} or 
making video games\cite{Guzdial2016}.
%
It is nearly hard to find a field where \gls{ai} isn't used in some way. 
This steady incorporation of \gls{ai} leads to the so called \gls{ai} effect\cite{McCorduck1982,ai100}: 
certain fields get incorporated into \gls{ai} research and practice,
such that after some time of general use it is no more considered \gls{ai} (e.g. spam filter or web searches).
Google CEO Sundar Pichai even goes as far and said: 
"AI is one of the most important things humanity is working on. It is more profound than [...] electricity or fire"\cite{Hassan2020}.

%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Machine Learning Methods}
%
\Gls{ml} is at the base of most \gls{ai}s.
It is an umbrella term for programs with instructions to learn from data, i.e. gain knowledge, categorise, predict and make decisions based on data. 
%
There is a platitude of different machine learning methods: 
they can be divided into supervised (training set is labeled) and unsupervised (exploratory).  
An orthogonal division can be made by regression (continuous data) versus classification (discrete, categorical data). 
Independent from these $2\times2$ categories there are multiple ways to let machines learn from data.
%
\Gls{nn} (one of the most popular architectures for big data\cite{Chiroma2019}) are loosely modeled after the brain\cite{bishop1994neural}.
Artificial neurons (also called nodes), which are arranged in layers, 
are connected to each of the neurons of previous and next layers
and the weights (parameters of intensity), with which the data is routed from one neuron to another, 
are optimised during training. 
%
Convolutional-layer \gls{nn} excel in picture recognition\cite{Lecun1995conv} and are useful in quantum mechanics too\cite{westermayr2020combining}.
Other common architectures include linear regression, kernel ridge regression and support vector regression.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Machine Learning and Statistics}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Why introduce machine learning to this project? 
%I wanted to apply and delve into what I've been studying during my undergrad courses. 
%This seemed like the perfect oppurtunity. 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Is machine learning just hyped statistics? No! 
		%{https://doi.org/10.1177\%2F1352458520978648}
		%{Machine and deep learning in MS research are just powerful statistics – No}
%What is \gls{ml}? 
Some might argue that \gls{ml} is just overglorified statistics, but that's not the case. 
Although \gls{ml} uses several statistical methods, their goal and frame conditions are different. 
%\td{The goal of machine learning is to ???}
%
\Gls{ml} tries to predict unseen data points accurately and statistics is a subfield of maths 
which tries to get insight into a given data. 
For example, in a statistical model, it is desirable to reduce the number of inputs. 
This allows a statistician to better study how a change in input variables can 
directly affect a output variable\cite{gontcharov2019}.
%pic from \url{https://towardsdatascience.com/notes-on-artificial-intelligence-ai-machine-learning-ml-and-deep-learning-dl-for-56e51a2071c2}
More precisely, mathematical statistics (stochastic)\cite{haertler2014statistisch} is the subject of 
finding mathematical models to describe the data 
whereas (classical) statistics is the domain of representing the data. 
Nonetheless, statistics and maths is at the very basis of \gls{ml}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Artificial Inteligence and Machine Learning}
%How can \gls{ai} and \gls{ml} be defined? 
\Gls{ai} is a trans-disciplinary field with roots in logic, statistics, cognitive psychology, decision theory, neuroscience, linguistics, cybernetics, and computer engineering\cite{howard2019artificial}.
The history of \gls{ai} goes back to the middle of the \nth{20} century. 
Researchers from the emerging field came together at the Dartmouth conference and the term "\gls{ai}" was coined\cite{McCarthy1955}. 
\Gls{ai}'s  history is beautifully depicted by McCorducks' 1982 book "Machines Who Think"\cite{McCorduck1982,Apter1982}, which focuses on the great minds behind the advances.
Pioneers like Alan Turing thought a lot about how to define, test and implement \gls{ai}\cite{howard2019artificial}. 
One example how to measure \gls{ai} is to let it play chess against a human\cite{Silver2017} 
(in 1997 a chess computer called Deep Blue won against the World Chess Champion Garry Kasparov for the first time\cite{Feng1999}).
Another test \textit{ingenioused} by Alan Turing is the imitation game\cite{turing1950imitation}, nowadays known as Turing test:
an interrogator communicates with two unknown entities \textbf{A} and \textbf{B} (a woman and a man) and must find out who is who. 
\textbf{A} will try to make to interrogator misjudge, whereas \textbf{B} is on the interrogators side.
The question is if \textbf{A} is replaced with a computer how the ratio of outcomes would deviate from the original ratio. 
%
At the moment it's hard to imagine a computer getting a higher ratio than a human
but when reading AI written articles\cite{gpt2020}, it's easy to see this test being passed in the near future; especially with ChatGPT's convincingly human-like answers\cite{dis2023chatgpt}.

But fear not, that doesn't mean that computers are 
more intelligent than humans
or \linebreak[4]
sentient\cite{searle1980,searle1999married} even though some claim\cite{tiku2022google} and it certainly does not mean that research is over. 
AI is still a young field, which is strongly growing and is gaining ubiquitous status. 
It is slowly creeping into every aspect of modern human life just like electricity around one hundred years ago. 
Realms in which AI is gaining traction are: 
%
playing board games (and beating humans)\cite{Silver2017,Feng1999,Campbell2002}, 
image recognition (very popular for medical diagnosis)\cite{Li2020,Deo2015,Topol2019,Fujiyoshi2019}, 
chemistry\cite{Westermayr2019,goh2017chemception,jha2018elemnet}, 
cyber security\cite{Sarker2021},
facial recognition (to prevent theft of toilet paper \cite{Andrews2017}),
financial sector (as robo-advisors)\cite{Littman2021},
natural language processing (NLP)\cite{Koroteev2021,Liu2021gpt,Parviainen2021} 
(which can also create code and pictures through scalable vector graphics (SVG))
and even creative tasks like 
creating non existing faces\cite{Mansourifar2020}, 
create graphic artwork (DALL-E 2)\cite{Marcus2022} or 
making video games\cite{Guzdial2016}.
%
It is nearly hard to find a field where \gls{ai} isn't used in some way. 
This steady incorporation of \gls{ai} leads to the so called \gls{ai} effect\cite{McCorduck1982,ai100}: 
certain fields get incorporated into \gls{ai} research and practice,
such that after some time of general use it is no more considered \gls{ai} (e.g. spam filter or web searches).
Google CEO Sundar Pichai even goes as far and said: 
"AI is one of the most important things humanity is working on. It is more profound than [...] electricity or fire"\cite{Hassan2020}.

%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Machine Learning Methods}
%
\Gls{ml} is at the base of most \gls{ai}s.
It is an umbrella term for programs with instructions to learn from data, i.e. gain knowledge, categorise, predict and make decisions based on data. 
%
There is a platitude of different machine learning methods: 
they can be divided into supervised (training set is labeled) and unsupervised (exploratory).  
An orthogonal division can be made by regression (continuous data) versus classification (discrete, categorical data). 
Independent from these $2\times2$ categories there are multiple ways to let machines learn from data.
%
\Gls{nn} (one of the most popular architectures for big data\cite{Chiroma2019}) are loosely modeled after the brain\cite{bishop1994neural}.
Artificial neurons (also called nodes), which are arranged in layers, 
are connected to each of the neurons of previous and next layers
and the weights (parameters of intensity), with which the data is routed from one neuron to another, 
are optimised during training. 
%
Convolutional-layer \gls{nn} excel in picture recognition\cite{Lecun1995conv} and are useful in quantum mechanics too\cite{westermayr2020combining}.
Other common methods include linear regression, kernel ridge regression and support vector regression.
